Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-04 manuscript-chicago.Rmd
Small edits

## Conclusion
Considering the pervasiveness of social media, it is unsurprising that social
activists and protesters have utilized these platforms to support real-world
mobilization. Here, we quantitatively explored the connection between online
social cohesion and real-world events. In addition to introducing political
scientists to a family of powerful nonlinear dynamics analyses, our results have
serious implications for monitoring global movements across other social
uprisings. While state-run media in regions of authoritarian rule are often
biased and serve as propaganda for the leader and central government, the
self-organized nature of Twitter provides a new avenue to gain insight into
truths about uprisings and social mobilization. By conceptualizing Twitter and
real-world events as two elements of an inextricably linked dynamical system,
the levels of social cohesion within social media platforms could be monitored
for fluctuations indicating shifts in power and peace. Social media mobilization
may thus help alert the world to citizens' actions and reactions that are
suppressed by government regimes, providing insight into events that may not
otherwise be broadcast and allowing for faster intervention.

>>>>

## Conclusion
Considering the pervasiveness of social media, it is unsurprising that social
activists and protesters have utilized these platforms to support real-world
mobilization. Here, we quantitatively explored the connection between online
social cohesion and real-world events. In addition to introducing political
scientists to a family of powerful nonlinear dynamics analyses, our results have
serious implications for monitoring global movements. While state-run media in
regions of authoritarian rule are often biased and serve as propaganda for the
leader and central government, the self-organized nature of Twitter provides a
new avenue to gain insight into truths about uprisings and social mobilization.
By conceptualizing Twitter and real-world events as two elements of an
inextricably linked dynamical system, the levels of social cohesion within
social media platforms could be monitored for fluctuations indicating shifts in
power and peace. Social media mobilization may thus help alert the world to
citizens' actions and reactions that are suppressed by government regimes,
providing insight into events that may not otherwise be broadcast and allowing
for faster intervention.
